Comparing Different Planned Missingness Designs in Longitudinal Studies

### 2018-05-22 Documentation/manuscript.Rnw
Manuscript changes.

\usepackage{graphicx}
\usepackage{mathptmx}      
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{cite}
\usepackage{caption}
\usepackage{natbib}

@@

Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are very aptly named. Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions. A common form setup is the three-form design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C. Each form of the survey includes the X block as well as two of the remaining blocks. This leaves the configurations seen in Table \ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded. Note that every block appears in at least one form. By designing the forms in this manner we are able to estimate the relationship between any chosen items regardless of their blocks. That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows this. \par

@@

<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig = TRUE>>=
require(gridExtra)
grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@

@@

names(df_8) <- c("Design", "Missingness", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
row.names(df_8) <- NULL
kable(df_8, escape = FALSE, format ="latex") %>%
  collapse_rows(columns = 1:2, latex_hline = "full")
  column_spec(1, width = "30em")

@@

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime1.RData")
low <- d

library(xtable)
print(xtable(cbind("","","",rbind(low[[1]],med[[1]],high[[1]],low[[2]],med[[2]],high[[2]],low[[3]],med[[3]],high[[3]])),digits= 3),include.rownames=FALSE)

@

>>>>

\usepackage{graphicx}
\usepackage{mathptmx}      
\usepackage{amsmath}
\usepackage{graphicx}
\usepackage{booktabs}
\usepackage{multirow}
\usepackage{cite}
\usepackage{caption}
\usepackage{natbib}
\usepackage{longtable}
\usepackage{array}
\usepackage[table]{xcolor}
\usepackage{wrapfig}
\usepackage{float}
\usepackage{colortbl}
\usepackage{pdflscape}
\usepackage{tabu}
% \usepackage{threeparttable}
% \usepackage{threeparttablex}
% \usepackage[normalem]{ulem}
% \usepackage{makecell}

@@

Split Form missingness designs \citep{raghunathan1995split}, also  known as Multi-Form \citep{little2013planned} or Matrix Sampling designs \citep{thomas2006evaluation}, are very aptly named. Instead of giving participants one large survey, researchers create multiple forms, each containing a subset of the full survey's questions. A common form setup is the three-form design \citep{graham1996maximizing} in which the full survey is split into four blocks: X, A, B, and C. Each form of the survey includes the X block as well as two of the remaining blocks. This leaves the configurations seen in Table \\ref{tab:table10}, where "1" indicates that the block is included and "0" indicates that it is excluded. Note that every block appears in at least one form. By designing the forms in this manner we are able to estimate the relationship between any chosen items regardless of their blocks. That is, if we want to estimate the relationship between an item in block A and another in C, there is a form that allows this. \par

@@

<<misslow, fig.cap = "Low missingness", echo = FALSE, message = FALSE, warning = FALSE, fig.keep = TRUE>>=
require(gridExtra)
grid.arrange(splitplot, alternatesplitplot, waveplot, ncol=3)
@

@@

names(df_8) <- c("Design", "Level", "Parameter", "Bias", "Pct Bias", "MSE", "Coverage", "CI Length", "FMI")
row.names(df_8) <- NULL
kable(df_8, escape = FALSE, format ="latex") %>%
  collapse_rows(columns = 1:2, latex_hline = "full") %>%
  kable_styling(latex_options = "scale_down")

@@

load("~/GitHub/designedmissingness/Results/tables20180509_60_1_low_hightime1.RData")
low <- d
@

### 2018-05-22 Documentation/manuscript.tex
Manuscript changes.

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}
\begin{tabular}{l|l|l|r|r|r|r|r|r}
\hline
Design & Missingness & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
\hline
 &  & $\gamma_0$ & 0.042 & -1.817 & 0.018 & 0.988 & 0.702 & 0.002\\
\cline{3-9}
 &  & $\beta_1$ & -0.071 & -25.122 & 0.269 & 0.983 & 2.534 & 0.236\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.253 & 0.024 & 0.932 & 0.585 & 0.000\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.886 & 0.000 & 0.944 & 0.017 & 0.001\\
\cline{2-9}
 &  & $\gamma_0$ & 0.039 & -1.684 & 0.018 & 0.990 & 0.709 & 0.011\\
\cline{3-9}
 &  & $\beta_1$ & -0.102 & -36.186 & 0.271 & 0.998 & 3.500 & 0.534\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.207 & 0.024 & 0.933 & 0.586 & 0.002\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.419 & 0.000 & 0.946 & 0.017 & 0.007\\
\cline{2-9}
 &  & $\gamma_0$ & 0.028 & -1.242 & 0.027 & 0.985 & 0.791 & 0.030\\
\cline{3-9}
 &  & $\beta_1$ & -0.107 & -38.054 & 0.418 & 0.988 & 4.268 & 0.630\\
\cline{3-9}
 &  & $\beta_2$ & 0.012 & 1.869 & 0.027 & 0.932 & 0.613 & 0.005\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.471 & 0.000 & 0.946 & 0.020 & 0.020\\
\cline{1-9}
 &  & $\gamma_0$ & 0.042 & -1.832 & 0.018 & 0.990 & 0.701 & 0.001\\
\cline{3-9}
 &  & $\beta_1$ & -0.069 & -24.401 & 0.283 & 0.983 & 2.508 & 0.218\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.272 & 0.024 & 0.933 & 0.585 & 0.000\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.949 & 0.000 & 0.944 & 0.017 & 0.001\\
\cline{2-9}
 &  & $\gamma_0$ & 0.040 & -1.760 & 0.018 & 0.988 & 0.704 & 0.007\\
\cline{3-9}
 &  & $\beta_1$ & -0.117 & -41.573 & 0.277 & 0.990 & 3.385 & 0.508\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.286 & 0.024 & 0.931 & 0.585 & 0.002\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.986 & 0.000 & 0.945 & 0.017 & 0.005\\
\cline{2-9}
 &  & $\gamma_0$ & 0.036 & -1.592 & 0.021 & 0.989 & 0.742 & 0.022\\
\cline{3-9}
 &  & $\beta_1$ & -0.158 & -56.111 & 0.394 & 0.992 & 4.336 & 0.662\\
\cline{3-9}
 &  & $\beta_2$ & 0.012 & 1.809 & 0.026 & 0.934 & 0.601 & 0.006\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.487 & 0.000 & 0.941 & 0.018 & 0.021\\
\cline{1-9}
 &  & $\gamma_0$ & 0.040 & -1.765 & 0.018 & 0.988 & 0.703 & 0.005\\
\cline{3-9}
 &  & $\beta_1$ & -0.094 & -33.425 & 0.238 & 0.993 & 2.995 & 0.433\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.251 & 0.024 & 0.934 & 0.585 & 0.001\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.875 & 0.000 & 0.943 & 0.017 & 0.002\\
\cline{2-9}
 &  & $\gamma_0$ & 0.028 & -1.223 & 0.018 & 0.995 & 0.744 & 0.051\\
\cline{3-9}
 &  & $\beta_1$ & -0.088 & -31.121 & 0.240 & 0.992 & 3.497 & 0.718\\
\cline{3-9}
 &  & $\beta_2$ & 0.009 & 1.436 & 0.024 & 0.933 & 0.588 & 0.006\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.326 & 0.000 & 0.946 & 0.017 & 0.025\\
\cline{2-9}
 &  & $\gamma_0$ & -0.004 & 0.194 & 0.020 & 0.995 & 0.962 & 0.224\\
\cline{3-9}
 &  & $\beta_1$ & -0.080 & -28.263 & 0.234 & 0.985 & 3.791 & 0.886\\
\cline{3-9}
 &  & $\beta_2$ & 0.011 & 1.700 & 0.024 & 0.938 & 0.607 & 0.032\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -3.304 & 0.000 & 0.970 & 0.020 & 0.148\\
\hline
\end{tabular}

\begin{kframe}

{\ttfamily\noindent\bfseries\color{errorcolor}{\#\# Error in column\_spec(1, width = "{}30em"{}): argument "{}column"{} is missing, with no default}}\begin{verbatim}
## % latex table generated in R 3.4.1 by xtable 1.8-2 package
## % Thu May 17 15:47:48 2018
## \begin{table}[ht]
## \centering
## \begin{tabular}{lllrrrrrr}
##   \hline
## "" & "" & "" & Coverage & Bias & MSE & FMI & CI Length & Pct Bias \\ 
##   \hline
##  &  &  & 0.968 & -0.023 & 0.120 & 0.018 & 1.414 & 0.498 \\ 
##    &  &  & 0.973 & 0.604 & 0.669 & 0.271 & 4.812 & 429.053 \\ 
##    &  &  & 0.955 & 0.010 & 0.048 & 0.003 & 0.827 & 3.263 \\ 
##    &  &  & 0.945 & -0.000 & 0.000 & 0.004 & 0.039 & -2.671 \\ 
##    &  &  & 0.972 & -0.048 & 0.128 & 0.059 & 1.506 & 1.060 \\ 
##    &  &  & 0.988 & 0.724 & 0.898 & 0.499 & 5.933 & 513.940 \\ 
##    &  &  & 0.958 & 0.025 & 0.047 & 0.013 & 0.834 & 7.927 \\ 
##    &  &  & 0.938 & -0.000 & 0.000 & 0.017 & 0.039 & -2.867 \\ 
##    &  &  & 0.984 & -0.178 & 0.370 & 0.132 & 2.050 & 3.882 \\ 
##    &  &  & 0.955 & 0.997 & 1.573 & 0.610 & 6.822 & 708.287 \\ 
##    &  &  & 0.965 & 0.044 & 0.060 & 0.036 & 0.966 & 13.650 \\ 
##    &  &  & 0.955 & -0.000 & 0.000 & 0.060 & 0.048 & -0.787 \\ 
##    &  &  & 0.966 & -0.019 & 0.119 & 0.011 & 1.401 & 0.415 \\ 
##    &  &  & 0.966 & 0.603 & 0.638 & 0.239 & 4.616 & 428.601 \\ 
##    &  &  & 0.956 & 0.014 & 0.048 & 0.002 & 0.827 & 4.254 \\ 
##    &  &  & 0.944 & -0.000 & 0.000 & 0.003 & 0.039 & -3.004 \\ 
##    &  &  & 0.978 & -0.045 & 0.124 & 0.053 & 1.493 & 0.988 \\ 
##    &  &  & 0.974 & 0.728 & 0.879 & 0.504 & 5.976 & 517.389 \\ 
##    &  &  & 0.954 & 0.024 & 0.051 & 0.011 & 0.838 & 7.437 \\ 
##    &  &  & 0.946 & -0.001 & 0.000 & 0.018 & 0.039 & -4.550 \\ 
##    &  &  & 0.984 & -0.117 & 0.196 & 0.112 & 1.759 & 2.557 \\ 
##    &  &  & 0.968 & 0.876 & 1.305 & 0.650 & 6.913 & 622.327 \\ 
##    &  &  & 0.963 & 0.026 & 0.051 & 0.034 & 0.892 & 8.265 \\ 
##    &  &  & 0.949 & -0.001 & 0.000 & 0.055 & 0.043 & -5.340 \\ 
##    &  &  & 0.968 & -0.057 & 0.127 & 0.038 & 1.454 & 1.249 \\ 
##    &  &  & 0.974 & 0.853 & 1.003 & 0.510 & 5.629 & 606.148 \\ 
##    &  &  & 0.959 & 0.006 & 0.046 & 0.006 & 0.831 & 1.804 \\ 
##    &  &  & 0.945 & -0.000 & 0.000 & 0.011 & 0.039 & -3.051 \\ 
##    &  &  & 0.979 & -0.182 & 0.166 & 0.183 & 1.813 & 3.981 \\ 
##    &  &  & 0.967 & 0.979 & 1.325 & 0.782 & 6.758 & 695.352 \\ 
##    &  &  & 0.956 & 0.020 & 0.050 & 0.037 & 0.871 & 6.425 \\ 
##    &  &  & 0.955 & -0.001 & 0.000 & 0.068 & 0.042 & -4.466 \\ 
##    &  &  & 0.987 & -0.403 & 0.345 & 0.440 & 2.789 & 8.803 \\ 
##    &  &  & 0.951 & 1.050 & 1.504 & 0.887 & 7.357 & 745.735 \\ 
##    &  &  & 0.973 & 0.019 & 0.050 & 0.099 & 0.960 & 5.848 \\ 
##    &  &  & 0.975 & -0.003 & 0.000 & 0.200 & 0.052 & -18.904 \\ 
##    \hline
## \end{tabular}
## \end{table}
\end{verbatim}
\end{kframe}
\end{knitrout}

>>>>

\begin{knitrout}
\definecolor{shadecolor}{rgb}{0.969, 0.969, 0.969}\color{fgcolor}\begin{table}[H]
\centering
\resizebox{\linewidth}{!}{\begin{tabular}{l|l|l|r|r|r|r|r|r}
\hline
Design & Level & Parameter & Bias & Pct Bias & MSE & Coverage & CI Length & FMI\\
\hline
 &  & $\gamma_0$ & 0.042 & -1.817 & 0.018 & 0.988 & 0.702 & 0.002\\
\cline{3-9}
 &  & $\beta_1$ & -0.071 & -25.122 & 0.269 & 0.983 & 2.534 & 0.236\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.253 & 0.024 & 0.932 & 0.585 & 0.000\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.886 & 0.000 & 0.944 & 0.017 & 0.001\\
\cline{2-9}
 &  & $\gamma_0$ & 0.039 & -1.684 & 0.018 & 0.990 & 0.709 & 0.011\\
\cline{3-9}
 &  & $\beta_1$ & -0.102 & -36.186 & 0.271 & 0.998 & 3.500 & 0.534\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.207 & 0.024 & 0.933 & 0.586 & 0.002\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.419 & 0.000 & 0.946 & 0.017 & 0.007\\
\cline{2-9}
 &  & $\gamma_0$ & 0.028 & -1.242 & 0.027 & 0.985 & 0.791 & 0.030\\
\cline{3-9}
 &  & $\beta_1$ & -0.107 & -38.054 & 0.418 & 0.988 & 4.268 & 0.630\\
\cline{3-9}
 &  & $\beta_2$ & 0.012 & 1.869 & 0.027 & 0.932 & 0.613 & 0.005\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -0.471 & 0.000 & 0.946 & 0.020 & 0.020\\
\cline{1-9}
 &  & $\gamma_0$ & 0.042 & -1.832 & 0.018 & 0.990 & 0.701 & 0.001\\
\cline{3-9}
 &  & $\beta_1$ & -0.069 & -24.401 & 0.283 & 0.983 & 2.508 & 0.218\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.272 & 0.024 & 0.933 & 0.585 & 0.000\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.949 & 0.000 & 0.944 & 0.017 & 0.001\\
\cline{2-9}
 &  & $\gamma_0$ & 0.040 & -1.760 & 0.018 & 0.988 & 0.704 & 0.007\\
\cline{3-9}
 &  & $\beta_1$ & -0.117 & -41.573 & 0.277 & 0.990 & 3.385 & 0.508\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.286 & 0.024 & 0.931 & 0.585 & 0.002\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -0.986 & 0.000 & 0.945 & 0.017 & 0.005\\
\cline{2-9}
 &  & $\gamma_0$ & 0.036 & -1.592 & 0.021 & 0.989 & 0.742 & 0.022\\
\cline{3-9}
 &  & $\beta_1$ & -0.158 & -56.111 & 0.394 & 0.992 & 4.336 & 0.662\\
\cline{3-9}
 &  & $\beta_2$ & 0.012 & 1.809 & 0.026 & 0.934 & 0.601 & 0.006\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Altered Split Form} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -1.487 & 0.000 & 0.941 & 0.018 & 0.021\\
\cline{1-9}
 &  & $\gamma_0$ & 0.040 & -1.765 & 0.018 & 0.988 & 0.703 & 0.005\\
\cline{3-9}
 &  & $\beta_1$ & -0.094 & -33.425 & 0.238 & 0.993 & 2.995 & 0.433\\
\cline{3-9}
 &  & $\beta_2$ & 0.008 & 1.251 & 0.024 & 0.934 & 0.585 & 0.001\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Low} & $\beta_3$ & 0.000 & -0.875 & 0.000 & 0.943 & 0.017 & 0.002\\
\cline{2-9}
 &  & $\gamma_0$ & 0.028 & -1.223 & 0.018 & 0.995 & 0.744 & 0.051\\
\cline{3-9}
 &  & $\beta_1$ & -0.088 & -31.121 & 0.240 & 0.992 & 3.497 & 0.718\\
\cline{3-9}
 &  & $\beta_2$ & 0.009 & 1.436 & 0.024 & 0.933 & 0.588 & 0.006\\
\cline{3-9}
 & \multirow{-4}{*}{\raggedright\arraybackslash Medium} & $\beta_3$ & 0.000 & -1.326 & 0.000 & 0.946 & 0.017 & 0.025\\
\cline{2-9}
 &  & $\gamma_0$ & -0.004 & 0.194 & 0.020 & 0.995 & 0.962 & 0.224\\
\cline{3-9}
 &  & $\beta_1$ & -0.080 & -28.263 & 0.234 & 0.985 & 3.791 & 0.886\\
\cline{3-9}
 &  & $\beta_2$ & 0.011 & 1.700 & 0.024 & 0.938 & 0.607 & 0.032\\
\cline{3-9}
\multirow{-12}{*}{\raggedright\arraybackslash Wave Missingness} & \multirow{-4}{*}{\raggedright\arraybackslash High} & $\beta_3$ & 0.000 & -3.304 & 0.000 & 0.970 & 0.020 & 0.148\\
\hline
\end{tabular}}
\end{table}
